Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards

### 2024-04-24 paper/paper.qmd
added models

@@

>>>>

## Model preduction

```{r}
#| echo: false
#| warning: false

test_maxey <- tibble(
  REB = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  AST = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  BLK = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  STL = c(
    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
  ),
  PTS = c(
    20, 25, 40, 30, 45, 20, 30, 35, 20, 15, 35, 30, 35, 20 
  )
)

view(test_maxey)

maxey_prediction <- predict(maxey_model, newdata = test_maxey)

```

```{r}
#| label: tbl-5
#| tbl-cap: This table is the prediction price of Tyrese Maxey RC Prizm Silver card using the model 
#| echo: false
#| warning: false

kable(maxey_prediction, padding = 5)

view(maxey_prediction)
```

@@

## Model Check

```{r}
library(rstanarm)

pp_check(maxey_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(maxey_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```
